\documentclass[paper=a4,fontsize=15pt]{scrartcl}

% packages
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[protrusion=true,expansion=true]{microtype}
\usepackage{graphicx}
\usepackage[svgnames]{xcolor}
\usepackage{geometry}
\usepackage{mfirstuc}
\usepackage{anyfontsize}
\usepackage{soul}
\usepackage{setspace}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{wrapfig}
\usepackage{sectsty}

\sectionfont{\fontsize{18}{10}\selectfont}

\titlespacing*{\section}
{0pt}{2.5ex plus 1ex minus .2ex}{1.2ex plus .2ex}

\pagestyle{empty}
\geometry{left=1.2cm, top=1cm, right=1.2cm, bottom=1cm, footskip=.5cm}

% set underscore \ul{} x pt below contents
\setul{2pt}{.4pt}

% set default font
\renewcommand{\familydefault}{\sfdefault}

% fat cdot
\makeatletter
\newcommand*\bigcdot{\mathpalette\bigcdot@{.5}}
\newcommand*\bigcdot@[2]{\mathbin{\vcenter{\hbox{\scalebox{#2}{$\m@th#1\bullet$}}}}}
\makeatother

% macros ------------------------------------------------------------------------------
% -------------------------------------------------------------------------------------

% helpers
\newcommand{\smolboispace}{\vspace*{0.1em}}
\newcommand{\quarterspace}{\vspace*{0.25em}}
\newcommand{\halfspace}{\vspace*{0.5em}}
\newcommand{\bighalfspace}{\vspace*{0.75em}}
\newcommand{\fullspace}{\vspace*{1em}}

% header
\newcommand{\http}[1]{\href{http://#1}{\ul{#1}}}
\newcommand{\https}[1]{\href{https://#1}{\ul{#1}}}
\newcommand{\email}[1]{\href{mailto:#1}{\ul{#1}}}

% skills
\newcommand*{\newsummary}[2]{
  \noindent\hangafter=0\small
  {\capitalisewords{\textbf{#1}}: #2 \par}
}

% document ----------------------------------------------------------------------------
% -------------------------------------------------------------------------------------
\begin{document}

\begin{center}
  {\fontsize{35}{40}\selectfont Lawrence Pan \par}
  \halfspace

  {\normalsize
    \email{lawrencefeipan@gmail.com}
    $\bigcdot$ \http{lpan.io}
    $\bigcdot$ \https{github.com/lpan}
    \par}
\end{center}

\newsummary{focus}{Distributed systems, Large-scale data processing/storage
  infrastructure}
\smolboispace
\newsummary{languages}{Scala, Java, Golang, Python, JavaScript, C/C++}

\section*{Experience}{}
\normalsize
\noindent \href{https://twitter.com}{\textbf{\ul{Twitter}}}
$\vert$ \small Software Engineering Intern
{\hfill \footnotesize \textit{May 2019 - Aug 2019}}
\begin{itemize}[noitemsep,leftmargin=20pt,label=\raisebox{0.25ex}{\tiny$\bullet$},topsep=5pt]
  \small
  \item Added support for \textit{end-to-end exactly-once processing} semantics
    in \href{https://apache.github.io/incubator-heron/}{\ul{Apache Heron}} by
    implementing a variant of the two-phase commit algorithm. Details in
    \href{https://docs.google.com/document/d/1Shqp2z-uAhsOUN2erbc2d-72wdjA8anp}{\ul{design
        doc}}.
  \item Designed and implemented a system (in Scala) that made Twitter's
    interactive query infrastructure (Presto and Hive) GDPR-compliant.
\end{itemize}

\bighalfspace
\normalsize
\noindent \href{https://plangrid.com}{\textbf{\ul{PlanGrid}}}
$\vert$ \small DevOps/Infrastructure Engineering Intern
{\hfill \footnotesize \textit{Sep 2018 - Dec 2018}}
\begin{itemize}[noitemsep,leftmargin=20pt,label=\raisebox{0.25ex}{\tiny$\bullet$},topsep=5pt]
  \small
  \item Implemented centralized authentication and path-based routing in
    PlanGrid's Kubernetes cluster using Envoy and Istio. This greatly improved
    developer productivity.
  \item Built Spinnaker pipelines to allow \textit{phased rollout} for
    ingress-related infrastructure changes.
  \item Contributed to the effort of instrumenting distributed tracing to
    improve visibility.
\end{itemize}

\bighalfspace
\normalsize
\noindent \href{https://datadoghq.com}{\textbf{\ul{Datadog}}}
$\vert$ \small Software Engineering Intern
{\hfill \footnotesize \textit{Jan 2018 - Apr 2018}}
\begin{itemize}[noitemsep,leftmargin=20pt,label=\raisebox{0.25ex}{\tiny$\bullet$},topsep=5pt]
  \small
  \item Worked on the metrics submission pipeline that streams millions of data
    points per second.
  \item Owned the time-series metadata creation service, written in Go, by
    ensuring its availability.
  \item Migrated the service's IPC layer to gRPC to improve reliability.
    Implemented consistent hashing and request termination, details in
    \href{http://lpan.io/migrating-to-grpc}{\ul{blog post}}.
\end{itemize}

\bighalfspace
\normalsize
\noindent \href{https://universe.com}{\ul{\textbf{Universe}}}
$\vert$ \small Software Engineering Intern (product)
{\hfill \footnotesize \textit{May 2017 - Aug 2017}}
\begin{itemize}[noitemsep,leftmargin=20pt,label=\raisebox{0.25ex}{\tiny$\bullet$},topsep=5pt]
  \small
  \item Developed many business-critical, A/B-tested, user-facing features
    using React and Rails.
  \item Pioneered and shipped Universe's first front-end app that consumes its
    new GraphQL API.
\end{itemize}

\bighalfspace
\normalsize
\noindent \href{https://plot.ly}{\textbf{\ul{Plotly}}}
$\vert$ \small Software Engineering Intern (product)
{\hfill \footnotesize \textit{May 2016 - Aug 2016}}
\begin{itemize}[noitemsep,leftmargin=20pt,label=\raisebox{0.25ex}{\tiny$\bullet$},topsep=5pt]
  \small
  \item Maintained and developed features for a
    \href{https://plot.ly/online-chart-maker/}{\ul{massive SaaS app}} built with
    React and Redux.
  \item Contributed to the development of an e2e testing framework written in
    Python Selenium.
\end{itemize}

\section*{Writings}{}
\begin{itemize}[noitemsep,leftmargin=20pt,label=\raisebox{0.25ex}{\tiny$\bullet$},topsep=5pt]
  \small
  \item \href{http://lpan.io/one-liner-dropbox-client}{\ul{My one-liner Dropbox
        client}} (\textbf{HackerNews front-paged})
  \item \href{http://lpan.io/what-i-learnt-from-viw}{\ul{Lessons learned from
        writing a text editor in C}} (\textbf{HackerNews front-paged})
  \item \href{http://lpan.io/migrating-to-grpc}{\ul{How gRPC helps improve
        reliability and fault tolerance at DataDog}}
\end{itemize}

\section*{Education}{}
\noindent \textbf{University of Waterloo} Bachelor of Software Engineering \par
\quarterspace
\footnotesize
\noindent \textit{Sep 2016 - May 2021 (expected)} \par
\noindent 90.3\% cumulative GPA, \textit{Dean's Honours List}

\end{document}
